EBASE manuscript

### 2022-12-16 manu-draft.qmd
working on summary table for apacmp

```

@@

* Comparison with Odum and BASEmetab: Fwoxy Appalachicola
* Comparison with Odum and BASemetab: Apalachicola, @fig-apacmp

@@

The common set of metabolic parameters returned by the Odum, BASEmetab, and EBASE methods are net ecosystem metabolism, gross production, respiration, and gas exchange.  Pairwise comparisons of the daily estimates returned by each method were evaluated using simple summary statistics including Pearson correlation coefficients and linear regression fits to evaluate potential biases in each method.  For the latter analysis, differences in intercept suggested an overall bias in magnitude, where differences in slope suggested a bias that depended on relative value of each observation (e.g., bias may differ between lower or higher values).  Comparisons were made for the whole year and by wet (June, July, August, September) or dry (all other months) season observations.  Results were also assessed separately for estimates based on the observed or detided disssolved oxygen time series.

@@

![Comparisons of daily metabolic estimates from the Odum, BASEmetab, and EBASE methods for one year of continuous monitoring data at Apalachicola Bay. Results for net ecosystem metabolism (NEM), gross production (P), respiration (R), and gas exchange (D) are compared using the (a) observed and (b) detided dissolved oxygen time series as input to each model.  All values are volumetric as mmol O$_2$ m$^3$ d$^{-1}$ and are grouped by the dry or wet season. Lines show the 1:1 comparison and the the Pearson correlation values are shown in parentheses for each facet title.](figs/apacmp.png){#fig-apacmp fig-align="center"}

@@

>>>>

load(file = here('tabs/apacmptab.RData'))
```

@@

* Comparison with Odum and BASEmetab: Fwoxy Appalachicola
* Comparison with Odum and BASemetab: Apalachicola, @fig-apacmpfig

@@

The common set of metabolic parameters returned by the Odum, BASEmetab, and EBASE methods are net ecosystem metabolism, gross production, respiration, and gas exchange.  Pairwise comparisons of the daily estimates returned by each method were evaluated using simple summary statistics including Pearson correlation coefficients and linear regression fits to evaluate potential biases in each method.  For the latter analysis, differences in intercept suggested an overall bias in magnitude, whereas the slope was further tested to determine if the estimate was significantly different than one, suggesting a bias that depended on relative value of each observation (e.g., bias may differ between lower or higher values).  Comparisons were made for the whole year and by wet (June, July, August, September) or dry (all other months) season observations.  Results were also assessed separately for estimates based on the observed or detided disssolved oxygen time series.

@@

![Comparisons of daily metabolic estimates from the Odum, BASEmetab, and EBASE methods for one year of continuous monitoring data at Apalachicola Bay. Results for net ecosystem metabolism (NEM), gross production (P), respiration (R), and gas exchange (D) are compared using the (a) observed and (b) detided dissolved oxygen time series as input to each model.  All values are volumetric as mmol O$_2$ m$^3$ d$^{-1}$ and are grouped by the dry or wet season. Black lines show the 1:1 comparison, the blue line shows the linea regression fit, and the Pearson correlation values are shown in parentheses for each facet title.](figs/apacmpfig.png){#fig-apacmpfig fig-align="center"}

@@

```{r}
#| tbl-cap: "Table 1: "  
# apacmptab
```
